flowCore: data structures package for flow cytometry data

### 2007-08-19 inst/doc/HowTo-flowCore.Rnw
remove parenId from class definition of gates
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@26510 bc3139a8-67e5-0310-9ffc-ced21a209358

The basic unit of manipulation in \Rpackage{flowCore} is the
\Rclass{flowFrame}, which corresponds roughly with a single
``FCS'' file exported from the flow cytometer's acquisition
software. At the moment we support FCS file versions 1.0
through 3.0, and we expect to support FCS4/ACS1 as soon as
the specification has been ratified.

@@

There are also several immediate processing options
available in this function, the most important of which is
the \Rfunction{transformation} parameter, which can either
``linearize'' (the default) or ``standardize'' our data. To
see how this works, first we will examine an FCS file
without any transformation at all:

@@

When only a particular subset of parameters is
desired the \Rfunction{column.pattern} parameter allows for
the specification of a regular expression and only
parameters that match the regular expression will be
included in the frame. For example, to include on the the
Height parameters:

@@

You can extract a \Rclass{flowFrame} from a \Rclass{flowSet} object in the usual way using the \Rfunction{[[} or \Rfunction{\$} extraction operators. On the other hand using he \Rfunction{[} extraction operator returns a new \Rclass{flowSet} by \textbf{copying} the environment. However, simply assigning the \Rclass{flowFrame} to a new variable will \textbf{not} copying the contained frames.

>>>>

The basic unit of manipulation in \Rpackage{flowCore} is the
\Rclass{flowFrame}, which corresponds roughly with a single
``FCS'' file exported from the flow cytometer's acquisition
software. At the moment we support FCS file versions 2.0
through 3.0, and we expect to support FCS4/ACS1 as soon as
the specification has been ratified.

@@

There are also several immediate processing options
available in this function, the most important of which is
the \Rfunction{transformation} parameter, which can either
``linearize'' (the default) or ``scale'' our data. To
see how this works, first we will examine an FCS file
without any transformation at all:

@@

When only a particular subset of parameters is
desired the \Rfunction{column.pattern} parameter allows for
the specification of a regular expression and only
parameters that match the regular expression will be
included in the frame. For example, to include on the Height parameters:

@@

You can extract a \Rclass{flowFrame} from a \Rclass{flowSet} object in the usual way using the \Rfunction{[[} or \Rfunction{\$} extraction operators. On the other hand using he \Rfunction{[} extraction operator returns a new \Rclass{flowSet} by \textbf{copying} the environment. However, simply assigning the \Rclass{flowFrame} to a new variable will \textbf{not} copy the contained frames.
